Supplementary information

### 2019-12-12 manuscript/supplementary.Rmd
improved descriptor info table

phenotypic_descriptor_info %>%
  kable(format = 'latex',booktabs = TRUE)
```

@@

site_correction_factors %>%
  mutate_if(is.double,signif,digits = 3) %>%
  kable(caption = 'Descriptor correction factors at each site')
```

>>>>

phenotypic_descriptor_info %>%
  kable(format = 'latex',booktabs = TRUE,longtable = TRUE) %>%
  kable_styling(latex_options = 'repeat_header',repeat_header_continued = TRUE) %>%
  column_spec(1,width = '1.5cm') %>%
  column_spec(2,width = '3cm') %>%
  column_spec(4:5,width = '7cm') %>%
  collapse_rows(columns = 1,latex_hline = "major", valign = "middle") %>%
  landscape()
```

@@

site_correction_factors %>%
  mutate_if(is.double,signif,digits = 3) %>%
  kable(format = 'latex',booktabs = TRUE,caption = 'Descriptor correction factors at each site') %>%
  collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```
